Scikit-learn: machine learning without learning the machinery

### 2014-07-03 article.tex
better defense of Python as implementation language
Speaking for myself at least, the problem with R and Weka is not
so much the statistics but the programming languages: R is a
poorly designed language, Weka uses two different interfaces
(GUI and Java).

I dropped Shogun because I'm not sure if it has the same audience
as the others. It seems to focus on kernel learning and very large
datasets.

\paragraph{Project vision.}
%
Scikit-learn was born from the observation that most standard
machine learning algorithms were out of reach of the users that could
most benefit from them: researchers --biologists, climate
scientists, experimental physicists-- or developers of web
services or domain-specific applications.
%
In the scientific world, implementations of these algorithms
mostly consisted of scattered pieces of code to download
on researchers' web pages. Unifying efforts could be found in
statistic-specific environments and libraries such as the R
language \cite{Rmanual}, the Weka Java library \cite{hall2009weka}, or
the Shogun C++ library \cite{sonnenburg2010}, but we felt that these were
too technical to reach our target users, not versed in statistics.

>>>>

\paragraph{Project vision.}
%
Scikit-learn was born from the observation that most standard
machine learning algorithms were out of reach of the users that could
most benefit from them: researchers --biologists, climate
scientists, experimental physicists-- or developers of web
services or domain-specific applications.
%
In the scientific world, implementations of these algorithms
mostly consisted of scattered pieces of code to download
on researchers' web pages. Unifying efforts could be found in
statistic-specific environments and libraries such as the R
language \cite{Rmanual} or the Weka Java toolkit \cite{hall2009weka}.
Of these, R is a custom \emph{language},
while Java is a library with a custom GUI.
The choice of Python ties machine learning into a general-purpose language
that allows interactive programming \cite{perez2007ipython},
with a single interface for
interactive work, scripting and full-blown applications.
